Windowed least-squares model reduction for dynamical systems

### 2019-10-12 main.tex
app c

@@

	argument, as it's a pair of arguments. You need to connect these by saying
	they associate with the same time-dependent funciton.} 
We introduce an arbitrary function $\variation : [0,T] \rightarrow \RR{M}$ with the boundary condition $\variationArg{0} = \bz$ and define a variation from the extremal by,

@@

The objective is to now find $\overline{\statez}$ that makes $\mathcal{J}_{\delta}$ stationary. This can be done by differentiating with respect to $\delta$, and setting the result to zero,% Noting that the extermum of Eq.~\ref{eq:el_gen} occurs when $\state = \state^*$, and thus when $\epsilon = 0$, we have,

@@

=  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \bigg) \variation(t) \bigg]dt + \\ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(T,\epsilon),\statezDotBar(T,\epsilon) ,T \big) \variation(T)  - \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(0,\epsilon),\statezDotBar(0,\epsilon) ,0\big) \variation(0) .
Noting that $\variationArg{0} = \bz$,

@@

=  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) , t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \bigg) \variation(t) \bigg]dt + \\ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(T,\epsilon),\statezDotBar(T,\epsilon) ,T \big) \variation(T) . 
Setting equal to zero to find the stationary points,

@@

By definition, we know $\statez(\cdot) \equiv \statezBar(\cdot;0)$ is a stationary point. Thus, setting $\epsilon = 0$,

@@

As $\variation$ is an arbitrary function, in order for the equality to hold we must have,

@@

\begin{equation}\label{eq:euler_lagrange_appendix}
\bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statez(t),\statezDot(t) ,t\big) \bigg]^T - \bigg[ \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statez(t),\statezDot(t),t \big) \bigg) \bigg]^T = \bz  
subject to,

@@

@@

Equation~\eqref{eq:euler_lagrange_appendix} is known as the Euler--Lagrange equation. It states that, if $\statez$ is an extremal of $\mathcal{J}$, then it must satisfy~\eqref{eq:euler_lagrange_appendix}. It is emphasized that~\eqref{eq:euler_lagrange_appendix} is a necessary condition on $\statez$ to make $\mathcal{J}$ stationary, but it is not a sufficient condition. It is additionally noted that~\eqref{eq:euler_lagrange_appendix} provides a stationary point of $\mathcal{J}$, but the resulting stationary point can be either a maximum or a minimum.

>>>>

	\KTC{In this section, $a$ and $b$ are sometimes used as time limits, while
	$0$ and $T$ are used elsewhere. Please go through carefully and make this
	consistent. I recommend using $a$ and $b$ because this is used within time
	windows.}
	\KTC{In this section, "extremum" is used a lot. You are just finding
	stationary points, which could be local minima, local maxima, or saddle
	points. Please avoid using "extemum" for this reason.} 

@@

	argument, as it's a pair of arguments. You need to connect these by defining
	a new function that maps a time-dependent function to this functional
	evaluated at the time-dependent function and its derivative..} 
We introduce an arbitrary function $\variation : [0,T] \rightarrow \RR{M}$
with the boundary condition $\variationArg{0} = \bz$ and define a variation
from the extremum by

@@

The objective is to now find $\overline{\statez}$ that makes
$\mathcal{J}_{\delta}$ stationary. This can be done by differentiating with
respect to $\delta$ and setting the result to zero, i.e., % Noting that the extermum of Eq.~\ref{eq:el_gen} occurs when $\state = \state^*$, and thus when $\epsilon = 0$, we have,
\begin{equation}\label{eq:stationaryOne}

@@

\begin{align}\label{eq:gradient}
	\begin{split}

@@

	=&  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete }
	\big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) , t \big)
	\variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial
	\stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon)
	,t \big) \bigg) \variation(t) \bigg]dt + \\ &\frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(T,\epsilon),\statezDotBar(T,\epsilon) ,T \big) \variation(T) . 
	\end{split}
where we have used $\variationArg{0} = \bz$.
Substituting Eq.~\eqref{eq:gradient} in the stationarity conditions~\eqref{eq:stationaryOne} yields
\begin{equation}\label{eq:statOne}

@@

By construction, $\statez(\cdot) \equiv \statezBar(\cdot;0)$ is a stationary
point; thus, setting $\epsilon = 0$ in Eq.~\eqref{eq:statOne} yields
\begin{equation}

@@

As $\variation$ is an arbitrary function, this equality requires

@@

\begin{gather}\label{eq:euler_lagrange_appendix}
\bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete }
	\big(\statez(t),\statezDot(t) ,t\big) \bigg]^T - \bigg[ \frac{d}{dt}\bigg(
	\frac{\partial \integrand}{\partial \stateyDotDiscrete }
	\big(\statez(t),\statezDot(t),t \big) \bigg) \bigg]^T = \bz  \\

@@

\end{gather}

@@

\KTC{I removed "subject to" as this is only used in an optimization-problem
statement. Also, I don't understand the $z(a) = z_a$ conditions, or how that
derives obviously from above. Can you clarify? Also note the inconsistent use
of $a$, $b$, and $0$, $T$.}
Equation~\eqref{eq:euler_lagrange_appendix} is known as the Euler--Lagrange
equation. It states that, if $\statez$ is an extremum of $\mathcal{J}$
\KTC{Again, note that $\mathcal J$ has two arguments, so it can't havec a
single vector servec as an extremum. Fix needed}, then it must
satisfy~\eqref{eq:euler_lagrange_appendix}. It is emphasized
that~\eqref{eq:euler_lagrange_appendix} is a necessary condition on $\statez$
to make $\mathcal{J}$ stationary, but it is not a sufficient condition. It is
additionally noted that~\eqref{eq:euler_lagrange_appendix} provides a
stationary point of $\mathcal{J}$, but the resulting stationary point can be
either a maximum or a minimum. \KTC{See above. Strictly, these could be local
minima, local maxima, or saddle points.}
